---
title: "Pipeline Failure Estimation"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Corrosion diagnostics

By using of `b31crvl()` simply imitate the output of *CRVL.BAS* which is the 
honored software for determining the allowable length and maximum allowable 
working pressure presented in 
[ASME B31G-1991](https://law.resource.org/pub/us/cfr/ibr/002/asme.b31g.1991.pdf):

```{r}
library(pipenostics)
    
b31crvl(
  maop = 910, d = 30, wth = .438, smys = 52000, def  = .72, depth = .1, l = 7.5
)
```

# Probability of failure

Let's consider a pipe in district heating network with

```{r}
diameter           <- 762         # [mm]
wall_thickness     <-  10         # [mm]
UTS                <- 434.3697    # [MPa]
```

which transfers heat-carrier (water) at

```{r}
operating_pressure <-   0.588399  # [MPa]
temperature        <-  95         # [°C]
```

During *inline inspection* four corroded areas (defects) are detected with:

```{r}
depth  <- c(2.45,  7.86,   7.93,   8.15)  # [mm]
```

whereas the length of all defects is not greater 200 mm:

```{r}
length <- rep(200, 4)  # [mm]
print(length)
```

Corrosion rates in radial and in longitudinal directions are not well-known and
may vary in range 0.01--0.30 mm/year:

```{r}
rar = function(n) stats::runif(n, .01, .30) / 365
ral = function(n) stats::runif(n, .01, .30) / 365
```

Then probabilities of failure (*POF*s) related to each corroded area are near:

```{r}
pof <- mepof(
  depth, length, rep(diameter, 4), rep(wall_thickness, 4),
  rep(UTS, 4), rep(operating_pressure, 4), rep(temperature, 4),
  rar, ral, method = "dnv"
)
```

So, the POF of the pipe is near

```{r}
print(max(pof))
```

The value of POF changes in time. So, in a year after *inline inspection* of
the pipe we can get something near

```{r}
pof <- mepof(
  depth, length, rep(diameter, 4), rep(wall_thickness, 4),
  rep(UTS, 4), rep(operating_pressure, 4), rep(temperature, 4),
  rar, ral, method = "dnv", days = 365
)
print(pof)
```

For entire pipe we get something near:

```{r}
print(max(pof))
```

Two years ago before *inline inspection* the pipe state was rather good:

```{r}
pof <- mepof(
  depth, length, rep(diameter, 4), rep(wall_thickness, 4),
  rep(UTS, 4), rep(operating_pressure, 4), rep(temperature, 4),
  rar, ral, method = "dnv", days = -2 * 365
)
print(pof)
```

For entire pipe we get something near:

```{r}
print(max(pof))
```

> &#8505;
  For underlying concepts and other usage examples refer to
  [Concepts and Useful Notes](pipenostics.html)
