---
title: "District Heating Regime Tracing"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Let's consider a tiny district heating model which consists with the next 
4-segment tracing path:

![<sup>*Figure: Regime tracing*</sup>](https://raw.githubusercontent.com/omega1x/pipenostics/a26e1171f05d3cd4f2c25a71ccde9947a095409f/.src/svg-graphics/m325regtrace.svg)

Suppose we have the next sensor readings for *forward tracing*:

```{r}
t_fw <- 130         # [°C]
p_fw <-   0.588399  # [MPa]
g_fw <- 250         # [ton/hour]
```

Let's discharges to network for each pipeline segment are somehow determined as

```{r}
discharges <- seq(0, 30, 10)  # [ton/hour]
print(discharges)
```

Then the calculated regime (red squares) for forward tracing is

```{r}
library(pipenostics)

regime_fw <- m325traceline(t_fw, p_fw, g_fw, discharges, forward = TRUE)
print(regime_fw)
```

> &#8505;
  Read [Concepts and useful notes](pipenostics.html) for a deeper dive into the
  topic.
